True versus apparent shapes of astrophysical bow shocks

### 2015-06-30 papers/Paper1/sec-generic-model.tex
New start on Jorge's paper
30/06/15 First attempt to write something in this section

\section{Conic section approximation to bow shock shapes}
\label{sec:conic}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:

>>>>

\section{Generic bow shock model}
\label{sec:generic-model}

The bow shocks we consider are originated by a source located at the origin, emitting a wind with a mass loss rate of $\dot{M}_w$ and a terminal
(supersonic) velocity $v_w$. This wind interacts with another wind originated by another source located at a distance $D$ from the first one. 
The mass loss rate of the second source is $\dot{M}_{w1}$ and the terminal velocity is $v_{w1}$. The momentum of the wind of the second source is
higher than the momentum of the first one, and the resultant bow shock is stationary due to pressure balance.
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "proplyd-bowshocks"
%%% End:
